---
title: "Contractor Business Data Report Dictionary CDRL"
output:
  word_document: default
  html_document:
    df_print: paged
version: 0.2.0
---

A. CONTRACT LINE ITEM NO.........: `r cdrl_clin_numb`  
B. EXHIBIT.......................: `r cdrl_exhibit`  
C. CATEGORY......................: Other.  
D. SYSTEM/ITEM...................: `r prime_mission_product`  
E. CONTRACT/PR NUMBER............: `r contract_numb`  
F. CONTRACTOR....................: `r contractor_name`  
G. PREPARED BY...................: `r cdrl_prepared_by`  
H. DATE..........................: `r cdrl_prepared_date`  
I. APPROVED BY...................: `r cdrl_approved_by`  
J. DATE..........................: `r cdrl_approved_date`  
01. DATA ITEM NUMBER.............: `r CBDR_CDRL_numb`  
02. TITLE OF DATA ITEM...........: `r CBDR_CDRL_title`  
03. SUBTITLE ....................: `r CBDR_CDRL_subtitle`  
04. AUTHORITY....................: `r CBDR_CDRL_did`(T) and see Block 16.  
05. CONTRACT REFERENCE...........:  
06. REQUIRING OFFICE.............:`r program_office_name_abbr`  
07. DD 250 REQ...................: See Block 16.  
08. APPROVAL CODE................: None.  
09. DIST. STATEMENT REQUIRED.....: `r CBDR_CDRL_dist`  
10. FREQUENCY....................: See Block 16.  
11. AS OF DATE...................: See Block 16.  
12. DATE OF FIRST SUBMISSION.....: See Block 16.  
13. DATE OF SUBSEQUENT SUBMISSION: See Block 16.  
14. DISTRIBUTION.................: See Block 16.  
15. TOTAL........................: See Block 16.  
16. REMARKS......................:  

```{r include=FALSE}
CDRL_did <- CBDR_CDRL_did
```

```{r child='cdrl_blocks/block04_csdr.Rmd'}
```

The Contractor Business Data Report is to be prepared by and for the business entity (e.g., plant, site, or business unit) responsible for submitting the Forward Pricing Rate Proposal (FPRP) representing the basis for Forward Pricing Rate Agreement (FPRA) negotiations with the government. In the absence of a FPR requirement, the term “FPR unit” shall be interpreted for reporting purposes as “business unit” as defined in the FAR.  

The required form and file type for each 1921-3 report is specified in `r CBDR_CDRL_did`.

```{r child='cdrl_blocks/block07_csdr.Rmd'}
```

```{r child='cdrl_blocks/block10-13_cbdr.Rmd'}
```

```{r child='cdrl_blocks/block14_csdr.Rmd'}
```

`r submission_instructions`  

17. PRICE GROUP..................: N/A
18. ESTIMATED TOTAL PRICE........: N/A
