---
title: "CSDR Dictionary CDRL"
output:
  word_document: default
  html_document:
    df_print: paged
version: 0.2.0
---

A. CONTRACT LINE ITEM NO.........: `r cdrl_clin_numb`  
B. EXHIBIT.......................: `r cdrl_exhibit`  
C. CATEGORY......................: Other.  
D. SYSTEM/ITEM...................: `r prime_mission_product`  
E. CONTRACT/PR NUMBER............: `r contract_numb`  
F. CONTRACTOR....................: `r contractor_name`  
G. PREPARED BY...................: `r cdrl_prepared_by`  
H. DATE..........................: `r cdrl_prepared_date`  
I. APPROVED BY...................: `r cdrl_approved_by`  
J. DATE..........................: `r cdrl_approved_date`  
01. DATA ITEM NUMBER.............: `r CDSR_CDRL_numb`  
02. TITLE OF DATA ITEM...........: `r CDSR_CDRL_title`  
03. SUBTITLE ....................: `r CDSR_CDRL_subtitle`  
04. AUTHORITY....................: `r CDSR_CDRL_did`(T) and see Block 16.  
05. CONTRACT REFERENCE...........:  
06. REQUIRING OFFICE.............: `r program_office_name_abbr`  
07. DD 250 REQ...................: See Block 16.  
08. APPROVAL CODE................: None.  
09. DIST. STATEMENT REQUIRED.....: `r CDSR_CDRL_dist`  
10. FREQUENCY....................: See Block 16.  
11. AS OF DATE...................: See Block 16.  
12. DATE OF FIRST SUBMISSION.....: See Block 16.  
13. DATE OF SUBSEQUENT SUBMISSION: See Block 16.  
14. DISTRIBUTION.................: See Block 16.  
15. TOTAL........................: See Attachment `r CSDR_plan_attch_numb` - CSDR Plan.  
16. REMARKS......................:  

```{r include=FALSE}
CDRL_did <- CDSR_CDRL_did
```

```{r child='cdrl_blocks/block04_csdr.Rmd'}
``` 

```{r child='cdrl_blocks/block07_csdr.Rmd'}
```

```{r child='cdrl_blocks/block10-13_csdr.Rmd'}
```

```{r child='cdrl_blocks/block14_csdr.Rmd'}
``` 

`r submission_instructions`  

17. PRICE GROUP..................: N/A
18. ESTIMATED TOTAL PRICE........: N/A
