---
title: "Quantity Data Report CDRL"
output:
  word_document: default
  html_document:
    df_print: paged
version: 0.2.0
---

A. CONTRACT LINE ITEM NO.........: `r cdrl_clin_numb`  
B. EXHIBIT.......................: `r cdrl_exhibit`  
C. CATEGORY......................: Other.  
D. SYSTEM/ITEM...................: `r prime_mission_product`  
E. CONTRACT/PR NUMBER............: `r contract_numb`  
F. CONTRACTOR....................: `r contractor_name`  
G. PREPARED BY...................: `r cdrl_prepared_by`  
H. DATE..........................: `r cdrl_prepared_date`  
I. APPROVED BY...................: `r cdrl_approved_by`  
J. DATE..........................: `r cdrl_approved_date`  
01. DATA ITEM NUMBER.............: `r QtyData_CDRL_numb`  
02. TITLE OF DATA ITEM...........: `r QtyData_CDRL_title`  
03. SUBTITLE ....................: `r QtyData_CDRL_subtitle`  
04. AUTHORITY....................: `r QtyData_CDRL_did`(T) and see Block 16.  
05. CONTRACT REFERENCE...........:   
06. REQUIRING OFFICE.............: `r program_office_name_abbr`  
07. DD 250 REQ...................: See Block 16.  
08. APPROVAL CODE................: None.  
09. DIST. STATEMENT REQUIRED.....: `r QtyData_CDRL_dist`  
10. FREQUENCY....................: See Block 16.  
11. AS OF DATE...................: See Block 16.  
12. DATE OF FIRST SUBMISSION.....: See Block 16.  
13. DATE OF SUBSEQUENT SUBMISSION: See Block 16.  
14. DISTRIBUTION.................: See Block 16.  
15. TOTAL........................: See Attachment `r CSDR_plan_attch_numb` - CSDR Plan.  
16. REMARKS......................:  

Block 04: The `r prime_vs_sub` shall develop, maintain, and deliver the data item in accordance with `r QtyData_CDRL_did`, the CSDR Manual (DoD Manual 5000.04), and as tailored in this CDRL and Attachment `r CSDR_plan_attch_numb` - CSDR Plan. The CSDR Manual is available from the CADE website at https://cade.osd.mil/.  

```{r include=FALSE}
CDRL_did <- QtyData_CDRL_did
```

```{r child='cdrl_blocks/block04_csdr.Rmd'}
```

The Quantity Date Report shall be delivered in either a) MS Excel (file extension ".xlsx") or comma separated values (file extension ".csv") in the `r prime_vs_sub`’s format of choosing, so long as it fulfills the requirements of the DD FORM 2794 as is in accordance with the Quantity Data Report DID (`r QtyData_CDRL_did`) or b) JavaScript Object Notation (JSON) as described in the Quantity Data Report Format Specification (FFS) and Data Exchange Instructions (DEI) referenced in the Quantity Data Report DID Requirements Section 2.  

```{r child='cdrl_blocks/block07_csdr.Rmd'}
```

```{r child='cdrl_blocks/block10-13_csdr.Rmd'}
```

```{r child='cdrl_blocks/block14_csdr.Rmd'}
```

`r submission_instructions`  

17. PRICE GROUP..................: N/A
18. ESTIMATED TOTAL PRICE........: N/A
