---
title: "Cost and Hour Report (FlexFile) CDRL"
output:
  word_document: default
  html_document:
    df_print: paged
version: 0.2.0
---

A. CONTRACT LINE ITEM NO.........: `r cdrl_clin_numb`  
B. EXHIBIT.......................: `r cdrl_exhibit`  
C. CATEGORY......................: Other.  
D. SYSTEM/ITEM...................: `r prime_mission_product`  
E. CONTRACT/PR NUMBER............: `r contract_numb`  
F. CONTRACTOR....................: `r contractor_name`  
G. PREPARED BY...................: `r cdrl_prepared_by`  
H. DATE..........................: `r cdrl_prepared_date`  
I. APPROVED BY...................: `r cdrl_approved_by`  
J. DATE..........................: `r cdrl_approved_date`  
01. DATA ITEM NUMBER.............: `r FlexFile_CDRL_numb`  
02. TITLE OF DATA ITEM...........: `r FlexFile_CDRL_title`  
03. SUBTITLE ....................: `r FlexFile_CDRL_subtitle`  
04. AUTHORITY....................: `r FlexFile_CDRL_did`(T) and see Block 16.  
05. CONTRACT REFERENCE...........:   
06. REQUIRING OFFICE.............: `r program_office_name_abbr`  
07. DD 250 REQ...................: See Block 16.  
08. APPROVAL CODE................: None.  
09. DIST. STATEMENT REQUIRED.....: `r FlexFile_CDRL_dist`  
10. FREQUENCY....................: See Block 16.  
11. AS OF DATE...................: See Block 16.  
12. DATE OF FIRST SUBMISSION.....: See Block 16.  
13. DATE OF SUBSEQUENT SUBMISSION: See Block 16.  
14. DISTRIBUTION.................: See Block 16.  
15. TOTAL........................: See Attachment `r CSDR_plan_attch_numb` - CSDR Plan.  
16. REMARKS......................:  

```{r include=FALSE}
CDRL_did <- FlexFile_CDRL_did
```

```{r child='cdrl_blocks/block04_csdr.Rmd'}
```

The `r prime_vs_sub` shall deliver this data item in one of the following formats: a) a stand-alone Microsoft Excel file (file extension ".xlsx"), b) a comma separated values (file extension ".csv") so long as the Excel or comma separated values submission fulfills the requirements of the DD FORM 2794 and is in accordance with the FlexFile DID (`r FlexFile_CDRL_did`), or c) JavaScript Object Notation (JSON) as described in the FlexFile File Format Specification (FFS) and Data Exchange Instructions (DEI) referenced in the FlexFile DID (`r FlexFile_CDRL_did`) Requirements Section 2. The FlexFile FFS and DEI are available at the CADE website at https://cade.osd.mil/policy then selecting "Data Item Descriptions and Forms".  

```{r child='cdrl_blocks/block07_csdr.Rmd'}
```

```{r child='cdrl_blocks/block10-13_csdr.Rmd'}
```

```{r child='cdrl_blocks/block14_csdr.Rmd'}
```

`r submission_instructions`  

17. PRICE GROUP..................: N/A
18. ESTIMATED TOTAL PRICE........: N/A
