---
title: Cost Reporting Scope of Work Template
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output:
  word_document: default
  html_document:
    df_print: paged
params:
  program_name_full:
    input: text
    label: "Full Program Name"
    value: ">>>program_name_full<<<"
  program_name_abbr:
    input: text
    label: "Abbreviated Program Name/Acronym"
    value: ">>>program_name_abbr<<<"
  program_office_name:
    input: text
    label: "Program Office Name"
    value: ">>>program_office_name<<<"
  program_office_name_abbr:
    input: text
    label: "Abbreviated Program Office Name"
    value: ">>>program_office_name_abbr<<<"
  prime_mission_product:
    input: text
    label: "System/Item Name"
    value: ">>>prime_mission_product<<<"
  prime_mission_product_abbr:
    input: text
    label: "Abbreviated System/Item Name"
    value: ">>>prime_mission_product_abbr<<<"
  program_ACAT:
    choices:
    - "ACAT-ID"
    - "ACAT-IC"
    - "ACAT-II"
    - "ACAT-III"
    - "ACAT-IV"
    - "Pre-ACAT"
    - "Other"
    - ">>>program_ACAT<<<"
    input: select
    label: "Program Acquisition Category"
    value: ">>>program_ACAT<<<"
  acqusition_phase_full:
    choices:
    - "Materiel Solution Analysis"
    - "Technology Maturation & Risk Reduction"
    - "Engineering & Manufacturing Development"
    - "Low Rate Initial Production"
    - "Full Rate Production"
    - "Operations & Sustainment"
    - "Pre-Materiel Solution Analysis"
    - "Middle Tier Acquisition - Rapid Prototyping"
    - "Middle Tier Acquisition - Rapid Fielding"
    - "Other Transaction Authority - Research Purpose"
    - "Other Transaction Authority - Prototype Purpose"
    - "Other Transaction Authority - Production Purpose"
    - "Multiple"
    - "TBD"
    - ">>>acqusition_phase_full<<<"
    input: select
    label: "Acquisition Phase"
    value: ">>>acqusition_phase_full<<<"
  acqusition_phase_abbr:
    choices:
    - "MSA"
    - "TMRR"
    - "EMD"
    - "LRIP"
    - "FRP"
    - "O&S"
    - "Pre-MSA"
    - "MTA - RP"
    - "MTA - RF"
    - "OTA - R"
    - "OTA - Proto"
    - "OTA - Prod"
    - "Multiple"
    - "TBD"
    - ">>>acqusition_phase_abbr<<<"
    input: select
    label: "Abbreviated Acquisition Phase"
    value: ">>>acqusition_phase_abbr<<<"
  approved_plan_numb:
    input: text
    label: "Approved CSDR Plan Number (Include Revision Number)"
    value: ">>>approved_plan_numb<<<"
  CSDR_plan_style:
    choices:
    - "FlexFile"
    - "Legacy"
    - ">>>CSDR_Plan_style<<<"
    input: select
    label: "FlexFile or Legacy CSDR Plan"
    value: ">>>CSDR_Plan_style<<<"
  CSDR_plan_std:
    choices:
    - "MIL-STD-881D"
    - "MIL-STD-881C"
    - "Other"
    - ">>>CSDR_plan_std<<<"
    input: select
    label: "MIL-STD-881 Utilized"
    value: ">>>CSDR_Plan_std<<<"
  CSDR_plan_commodity_type:
    choices:
      - "Aircraft System (MIL-STD-881D)"
      - "Electronic System/Generic System (MIL-STD-881D)"
      - "Missile/Ordnance System (MIL-STD-881D)"
      - "Strategic Missile Systems (MIL-STD-881D)"
      - "Sea System (MIL-STD-881D)"
      - "Space System (MIL-STD-881D)"
      - "Ground Vehicle System (MIL-STD-881D)"
      - "Unmanned Maritime System (MIL-STD-881D)"
      - "Launch Vehicle System (MIL-STD-881D)"
      - "Information Systems (IS)/Defense Business Systems (DBS) (Investment) (MIL-STD-881D)"
      - "Aircraft System (MIL-STD-881C)"
      - "Electronic Systems (MIL-STD-881C)"
      - "Missile Systems (MIL-STD-881C)"
      - "Ordnance Systems (MIL-STD-881C)"
      - "Sea Systems (MIL-STD-881C)"
      - "Space Systems (MIL-STD-881C)"
      - "Surface Vehicle Systems (MIL-STD-881C)"
      - "Unmanned Air Vehicle Systems (MIL-STD-881C)"
      - "Unmanned Maritime Systems (MIL-STD-881C)"
      - "Launch Vehicle Systems (MIL-STD-881C)"
      - "Automated Information Systems (MIL-STD-881C)"
      - "Other"
      - ">>>CSDR_plan_commodity_type<<<"
    input: select
    label: "CSDR Plan Commodity Type"
    value: ">>>CSDR_plan_commodity_type<<<"
  CSDR_plan_org_name:
    input: text
    label: "Preparing USG Organization’s Name"
    value: ">>>CSDR_plan_org_name<<<"
  CSDR_plan_POC_name:
    input: text
    label: "POC Name (Last, First, M.)"
    value: ">>>CSDR_plan_POC_name<<<"
  CSDR_plan_POC_address:
    input: text
    label: "POC Address (Include ZIP Code)"
    value: ">>>CSDR_plan_POC_address<<<"
  CSDR_plan_POC_phone:
    input: text
    label: "POC Telephone Number"
    value: ">>>CSDR_plan_POC_phone<<<"
  CSDR_plan_POC_extension:
    input: text
    label: "POC Telephone Extension"
    value: ">>>CSDR_plan_POC_extension<<<"
  CSDR_plan_POC_email:
    input: text
    label: "POC Email Address"
    value: ">>>CSDR_plan_POC_email<<<"
  solicitation_numb:
    input: text
    label: "Solicitation Number"
    value: ">>>solicitation_numb<<<"
  contract_numb:
    input: text
    label: "Contract Number"
    value: ">>>contract_numb<<<"
  reporting_organization_type:
    choices:
    - "Prime Contractor"
    - "Subcontractor"
    - "Government"
    - ">>>reporting_organization_type<<<"
    input: select
    label: "Reporting Organization Type"
    value: ">>>reporting_organization_type<<<"
  contractor_name:
    input: text
    label: "Reporting Organization’s Name"
    value: ">>>contractor_name<<<"
  contractor_name_abbr:
    input: text
    label: "Abbreviated Reporting Organization’s Name"
    value: ">>>contractor_name_abbr<<<"
  draft_RFP_release_date:
    input: date
    label: "Draft RFP Release Date"
    value: !r Sys.Date()
  RFP_release_date:
    input: date
    label: "Final RFP Release Date"
    value: !r Sys.Date()
  contract_award_date:
    input: date
    label: "Target Contract Award Date"
    value: !r Sys.Date()
  contract_end_date:
    input: date
    label: "Estimated Contract Complete Date"
    value: !r Sys.Date()
  est_contract_value:
    input: numeric
    label: "Estimated Total Contract Value"
    value: ">>>est_contract_value<<<"
  est_contract_swdev_value:
    input: numeric
    label: "Estimated Total Value of Software Development Scopes of Work"
    value: ">>>est_contract_swdev_value<<<"
  est_contract_swmx_value:
    input: numeric
    label: "Estimated Total Value of Software Maintenance Scopes of Work"
    value: ">>>est_contract_swmx_value<<<"
  est_contract_sys_value:
    input: numeric
    label: "Estimated Total Value of Sustainment Scopes of Work"
    value: ">>>est_contract_sys_value<<<"
  pco_name:
    input: text
    label: "PCO Name"
    value: ">>>pco_name<<<"
  pco_email:
    input: text
    label: "PCO Email Address?"
    value: ">>>pco_email<<<"
  pco_phone:
    input: text
    label: "PCO Phone Number"
    value: ">>>pco_phone<<<"
  cost_rep_sow_numb:
    input: text
    label: "Cost Reporting Paragraph Number"
    value: ">>>cost_rep_sow_numb<<<"
  RDT_CDRL_lgl:
    choices:
      - TRUE
      - FALSE
    input: select
    label: "Resource Distribution Table (RDT) CDRL Required"
    value: TRUE
  FlexFile_CDRL_lgl:
    choices:
      - TRUE
      - FALSE
    input: select
    label: "Cost and Hour Report (FlexFile) CDRL Required"
    value: TRUE
  QtyData_CDRL_lgl:
    choices:
      - TRUE
      - FALSE
    input: select
    label: "Quantity Data Report CDRL Required"
    value: TRUE
  MR_CDRL_lgl:
    choices:
      - TRUE
      - FALSE
    input: select
    label: "Maintenance and Repair Report CDRL Required"
    value: TRUE
  TDR_CDRL_lgl:
    choices:
      - TRUE
      - FALSE
    input: select
    label: "Technical Data Report CDRL Required"
    value: TRUE
  CWBS_CDRL_lgl:
    choices:
      - TRUE
      - FALSE
    input: select
    label: "Contract Work Breakdown Structure (CWBS) Dictionary CDRL Required"
    value: TRUE
  CDSR_CDRL_lgl:
    choices:
      - TRUE
      - FALSE
    input: select
    label: "Cost Data Summary Report (DD Form 1921) CDRL Required"
    value: TRUE
  FCHR_CDRL_lgl:
    choices:
      - TRUE
      - FALSE
    input: select
    label: "Functional Cost-Hour Report (DD Form 1921-1) CDRL Required"
    value: TRUE
  PCR_CDRL_lgl:
    choices:
      - TRUE
      - FALSE
    input: select
    label: "Progress Curve Report (DD Form 1921-2) CDRL Required"
    value: TRUE
  CBDR_CDRL_lgl:
    choices:
      - TRUE
      - FALSE
    input: select
    label: "Contractor Business Data Report (DD Form 1921-3) CDRL Required"
    value: TRUE
  SFCHR_CDRL_lgl:
    choices:
      - TRUE
      - FALSE
    input: select
    label: "Sustainment Functional Cost-Hour Report (DD Form 1921-5) CDRL Required"
    value: TRUE
  SDR_CDRL_lgl:
    choices:
      - TRUE
      - FALSE
    input: select
    label: "Software Development Report (DD Form 3026-1) CDRL Required"
    value: TRUE
  SMR_CDRL_lgl:
    choices:
      - TRUE
      - FALSE
    input: select
    label: "Software Maintenance Report (DD Form 3026-2) CDRL Required"
    value: TRUE
  ERP_CDRL_lgl:
    choices:
      - TRUE
      - FALSE
    input: select
    label: "Enterprise Resource Planning (ERP) Software Development Report (DD Form 3026-3) CDRL Required"
    value: TRUE
  BOM_CDRL_lgl:
    choices:
      - TRUE
      - FALSE
    input: select
    label: "Bill of Materials (BOM) Report CDRL Required"
    value: TRUE
  LSPD_CDRL_lgl:
    choices:
      - TRUE
      - FALSE
    input: select
    label: "Lot Size Pricing Data (LSPD) CDRL Required"
    value: TRUE
  AUMC_CDRL_lgl:
    choices:
      - TRUE
      - FALSE
    input: select
    label: "Average Unit Manufacturing Cost (AUMC) Report CDRL Required"
    value: TRUE
  CFSR_CDRL_lgl:
    choices:
      - TRUE
      - FALSE
    input: select
    label: "Contractor Funds Status Report (CFSR) CDRL Required"
    value: TRUE
  PaCR_CDRL_lgl:
    choices:
      - TRUE
      - FALSE
    input: select
    label: "Performance & Cost Report (P&CR) CDRL Required"
    value: TRUE
  PAC_CDRL_lgl:
    choices:
      - TRUE
      - FALSE
    input: select
    label: "Post Award Conference Materials CDRL Required"
    value: TRUE
  cdrl_clin_numb:
    input: text
    label: "Contract Data Requirements List (CDRL) CLIN Number"
    value: ">>>cdrl_clin_numb<<<"
  cdrl_exhibit:
    choices: [A, B, C, D, E, F, G, H, I, J, K, L, M, N, O, P, Q, R, S, T, U, V, W, X, Y, Z, ">>>cdrl_exhibit<<<"]
    input: select
    label: "Contract Data Requirements List (CDRL) Exhibit Letter"
    value: ">>>cdrl_exhibit<<<"
  RDT_CDRL_numb:
    input: text
    label: "Resource Distribution Table CDRL Number"
    value: ">>>RDT_CDRL_numb<<<"
  FlexFile_CDRL_numb:
    input: text
    label: "Cost and Hour Report (FlexFile) CDRL Number"
    value: ">>>FlexFile_CDRL_numb<<<"
  QtyData_CDRL_numb:
    input: text
    label: "Quantity Data Report CDRL Number"
    value: ">>>QtyData_CDRL_numb<<<"
  MR_CDRL_numb:
    input: text
    label: "Maintenance and Repair Report CDRL Number"
    value: ">>>MR_CDRL_numb<<<"
  TDR_CDRL_numb:
    input: text
    label: "Technical Data Report CDRL Number"
    value: ">>>TDR_CDRL_numb<<<"
  CWBS_CDRL_numb:
    input: text
    label: "Contract Work Breakdown Structure and Dictionary CDRL Number"
    value: ">>>CWBS_CDRL_numb<<<"
  CDSR_CDRL_numb:
    input: text
    label: "Cost Data Summary Report (DD Form 1921) CDRL Number"
    value: ">>>CDSR_CDRL_numb<<<"
  FCHR_CDRL_numb:
    input: text
    label: "Functional Cost-Hour Report (DD Form 1921-1) CDRL Number"
    value: ">>>FCHR_CDRL_numb<<<"
  PCR_CDRL_numb:
    input: text
    label: "Progress Curve Report (DD Form 1921-2) CDRL Number"
    value: ">>>PCR_CDRL_numb<<<"
  CBDR_CDRL_numb:
    input: text
    label: "Contractor Business Data Report (DD Form 1921-3) CDRL Number"
    value: ">>>CBDR_CDRL_numb<<<"
  SFCHR_CDRL_numb:
    input: text
    label: "Sustainment Functional Cost-Hour Report (DD Form 1921-5) CDRL Number"
    value: ">>>SFCHR_CDRL_numb<<<"
  SDR_CDRL_numb:
    input: text
    label: "Software Development Report (DD Form 3026-1) CDRL Number"
    value: ">>>SDR_CDRL_numb<<<"
  SMR_CDRL_numb:
    input: text
    label: "Software Maintenance Report (DD Form 3026-2) CDRL Number"
    value: ">>>SMR_CDRL_numb<<<"
  ERP_CDRL_numb:
    input: text
    label: "Enterprise Resource Planning (ERP) Software Development Report (DD Form 3026-3) CDRL Number"
    value: ">>>ERP_CDRL_numb<<<"
  BOM_CDRL_numb:
    input: text
    label: "Bill of Materials (BOM) Report CDRL Number"
    value: ">>>BOM_CDRL_NUMB<<<"
  LSPD_CDRL_numb:
    input: text
    label: "Lot Size Pricing Data (LSPD) CDRL Number"
    value: ">>>LSPD_CDRL_numb<<<"
  AUMC_CDRL_numb:
    input: text
    label: "Average Unit Manufacturing Cost (AUMC) Report CDRL Number"
    value: ">>>AUMC_CDRL_numb<<<"
  CFSR_CDRL_numb:
    input: text
    label: "Contractor Funds Status Report (CFSR) CDRL Number"
    value: ">>>CFSR_CDRL_numb<<<"
  PaCR_CDRL_numb:
    input: text
    label: "Performance & Cost Report (P&CR) CDRL Number"
    value: ">>>PaCR_CDRL_numb<<<"
  PAC_CDRL_numb:
    input: text
    label: "Post Award Conference Materials CDRL Number"
    value: ">>>PAC_CDRL_numb<<<"
  cdrl_prepared_by:
    input: text
    label: "First & Last Name, Title of CDRL Preparer"
    value: ">>>John Doe, Operations Research Analyst<<<"
  cdrl_prepared_date:
    input: date
    label: "CDRL Prepared Date"
    value: !r Sys.Date()
  cdrl_approved_by:
    input: text
    label: "First & Last Name, Title of CDRL Approver"
    value: ">>>Jane Doe, Chief Operations Research Analyst<<<"
  cdrl_approved_date:
    input: date
    label: "CDRL Approved Date"
    value: !r Sys.Date()
  submission_instructions:
    input: text
    label: "Additional Submission Instructions"
    value: ">>>submission_instructions<<<"
  CSDR_plan_attch_numb:
    input: text
    label: "CSDR Plan Attachment Number"
    value: ">>>CSDR_plan_attch_numb<<<"
  RDT_attach_numb:
    input: text
    label: "Resource Distribution Table Attachment Number"
    value: ">>>RDT_attach_numb<<<"
  LSPD_attach_numb:
    input: text
    label: "Lot Size Pricing Data Attachment Number"
    value: ">>>LSPD_attach_numb<<<"
  AUMC_attach_numb:
    input: text
    label: "Average Unit Manufacturing Cost Report Attachment Number"
    value: ">>>AUMC_attach_numb<<<"
  readiness_review_required:
    choices:
      - TRUE
      - FALSE
    input: select
    label: "CSDR Readiness Review Required?"
    value: FALSE
version: 0.22.0
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
# Find what: (\>\>\>)*(\<\<\<)
# make sure "Use widecards" is checked
# Click in "Replace with:" select "Format" select "Font" then "Font color:" then select red. 
```

### Cost and Software Data Reporting (CSDR)
Cost and Software Data are the primary means by which the Department of Defense (DoD) collects data on the costs that contractors incur on DoD programs. Reliable and comprehensive cost data is essential to produce credible cost estimates as required in both statute and regulation. The Government's goals and use of CSDR data is to improve the quality of cost estimates; ensure proper resource allocation occurs within the DoD; and enable data driven decision making by program and department leadership.  

The `r prime_vs_sub` shall systematically collect and report actual contract costs in accordance with the following Contract Data Requirements Lists (CDRLs) and Attachment `r params$CSDR_plan_attch_numb`, the "Contract Cost and Software Data Reporting (CSDR) Plan":  

| Report Title                                                                    |             CDRL              |
| :------------------------------------------------------------------------------ | :---------------------------: |
| Resource Distribution Table                                                     |   `r params$RDT_CDRL_numb`    |
| Cost and Hour Report (FlexFile)                                                 | `r params$FlexFile_CDRL_numb` |
| Quantity Data Report                                                            |   `r params$QtyData_CDRL_numb`|
| Maintenance and Repair Report                                                   |    `r params$MR_CDRL_numb`    |
| Technical Data Report                                                           |   `r params$TDR_CDRL_numb`    |
| Contract Work Breakdown Structure and Dictionary                                |   `r params$CWBS_CDRL_numb`   |
| Cost Data Summary Report (DD Form 1921)                                         |   `r params$CDSR_CDRL_numb`   |
| Functional Cost-Hour Report (DD Form 1921-1)                                    |   `r params$FCHR_CDRL_numb`   |
| Progress Curve Report (DD Form 1921-2)                                          |   `r params$PCR_CDRL_numb`    |
| Contractor Business Data Report (DD Form 1921-3)                                |   `r params$CBDR_CDRL_numb`   |
| Sustainment Functional Cost-Hour Report (DD Form 1921-5)                        |  `r params$SFCHR_CDRL_numb`   |
| Software Development Report (DD Form 3026-1)                                    |   `r params$SDR_CDRL_numb`    |
| Software Maintenance Report (DD Form 3026-2)                                    |   `r params$SMR_CDRL_numb`    |
| Enterprise Resource Planning (ERP) Software Development Report (DD Form 3026-3) |   `r params$ERP_CDRL_numb`    |
| Bill of Materials (BOM)                                                         |   `r params$BOM_CDRL_numb`    |
| Lot Size Pricing Data (LSPD)                                                    |   `r params$LSPD_CDRL_numb`   |
| Average Unit Manufacturing Cost (AUMC) Report                                   |   `r params$AUMC_CDRL_numb`   |
| Contract Funds Status Report (CFSR) (DD Form 1586)                              |   `r params$CFSR_CDRL_numb`   |
| Performance and Cost Report (P&CR)                                              |   `r params$PaCR_CDRL_numb`   |
| Post Award Conference Materials                                                 |   `r params$PAC_CDRL_numb`    |

#### Application to Subcontractors
```{r , eval=FALSE, echo=FALSE}
# TODO: Need to automatically identify $20M vs. $50M and MTA memo vs. 5000 as the subcontractor reporting threshold.
```
The `r prime_vs_sub` shall flow down CSDR requirements referenced in section `r params$cost_rep_sow_numb` and its sub-paragraphs to subcontractors (regardless of subcontractor tier) when the subcontract value is expected to exceed \$20 million using the maximum allowable contract quantities, hours, or options (as applicable), as required by Department of Defense (DoD) 5000.04-M-1 - CSDR Manual. The Contractor shall require subcontractors to electronically submit CSDRs deliverables directly to the Defense Cost and Resource Center (DCARC). The Contractor shall ensure that Subcontractors subject to CSDR reporting thresholds collect data in sufficient detail to meet Attachment `r params$CSDR_plan_attch_numb` - CSDR Plan requirements. The Contractor shall collect and deliver data on all subcontractors to comply with Attachment `r params$RDT_attach_numb` and CDRL `r params$RDT_CDRL_numb` - Resource Distribution Table and Attachment `r params$CSDR_plan_attch_numb` - CSDR Plan requirements. A “subcontract” is any agreement, purchase order, or instrument other than a prime contract calling for work or for the material required for the performance of one or more prime contracts. A “subcontract” usually covers procurement of major components or subsystems that require the subcontractor to do extensive design, development, engineering, and testing to meet a prime contractor’s procurement specifications.   

#### Resource Distribution Table (RDT)
The `r prime_vs_sub` shall prepare and submit the "Resource Distribution Table (RDT)" in accordance with CDRL `r params$RDT_CDRL_numb`. The "Resource Distribution Table (RDT)" identifies the value of work assigned to the Contractor and its subcontractors by for each WBS element listed in Attachment `r params$CSDR_plan_attch_numb` - CSDR Plan, and is the primary means of identifying subcontractors who qualify for CSDR reporting.  

#### Contract Work Breakdown Structure (WBS) & Dictionary
```{r , eval=FALSE, echo=FALSE}
# TODO: Needs to be its own paragraph in legacy but needs to be nested under FlexFile if FF. I think the requirements may be slightly different under FlexFile as well.
```
The `r prime_vs_sub` shall utilize the Contract Work Breakdown Structure (WBS) identified in Attachment `r params$CSDR_plan_attch_numb` - CSDR Plan, as the primary framework for contract budgeting and reporting of incurred costs and hours to perform the contract. The `r prime_vs_sub` shall extend the WBS to provide adequate internal management, surveillance, and performance measurement of the contract. The Contractor shall ensure all WBS oriented reporting is compliant with at least the levels identified in Attachment `r params$CSDR_plan_attch_numb` - CSDR Plan. The `r prime_vs_sub` shall develop and maintain a "Contract Work Breakdown Structure (CWBS) Dictionary" throughout the life of the contract, and shall submit the "CWBS Dictionary" IAW CDRL `r params$CWBS_CDRL_numb`. The "CWBS Dictionary" reports a description of the technical, cost, and work content of each WBS element.  

#### Cost and Hour Report (FlexFile)
The `r prime_vs_sub` shall prepare and submit the "Cost and Hour Report (FlexFile)" in accordance with CDRL `r params$FlexFile_CDRL_numb`. The "Cost and Hour Report (FlexFile)" reports incurred and forecasted costs and hours related business data in order to perform this contract.  

#### Quantity Data Report  
The `r prime_vs_sub` shall prepare and submit the "Quantity Data Report" in accordance with CDRL `r params$QtyData_CDRL_numb`. The "Quantity Data Report" reports quantity information to provide context to the data reported in FlexFile submissions and in order to derive accurate unit cost information.  

#### Cost Data Summary Report (CDSR, DD Form 1921)
The `r prime_vs_sub` shall prepare and submit the "Cost Data Summary Report (DD Form 1921)" in accordance with CDRL `r params$CDSR_CDRL_numb`. The "Cost Data Summary Report (DD Form 1921)" reports actual and forecasted cost and quantity data by WBS element specified in Attachment `r params$CSDR_plan_attch_numb` - CSDR Plan.  

#### Functional Cost-Hour Report (FCHR, DD Form 1921-1)
The `r prime_vs_sub` shall prepare and submit the "Functional Cost-Hour Report (DD Form 1921-1)" in accordance with CDRL `r params$FCHR_CDRL_numb`. The "Functional Cost-Hour Report (DD Form 1921-1)" reports information on actual and forecasted production labor hours, overhead costs, material costs, and other direct and indirect costs by WBS element specified in Attachment `r params$CSDR_plan_attch_numb` - CSDR Plan.  

#### Progress Curve Report (PCR, DD Form 1921-2)
The `r prime_vs_sub` shall prepare and submit "Progress Curve Report (DD Form 1921-2)" in accordance with CDRL `r params$PCR_CDRL_numb`. The "Progress Curve Report (DD Form 1921-2)" reports actual production cost and hours data at the unit or sub-lot level, as specified in Attachment `r params$CSDR_plan_attch_numb` - CSDR Plan.  

#### Contractor Business Data Report (CBDR, DD Form 1921-3)
The `r prime_vs_sub` shall prepare and submit the "Contractor Business Data Report (DD Form 1921-3)" in accordance with CDRL `r params$CBDR_CDRL_numb`. The "Contractor Business Data Report (DD Form 1921-3)" reports data to facilitate estimating and analysis of indirect contract costs and rates.  

#### Sustainment Functional Cost-Hour Report (SFCHR)
The `r prime_vs_sub` shall prepare and submit the "Sustainment Functional Cost-Hour Report (DD Form 1921-5)" in accordance with CDRL `r params$MR_CDRL_numb`. The "Sustainment Functional Cost-Hour Report (DD Form 1921-5)" reports information on actual and forecasted sustainment labor hours, overhead costs, material costs, and other direct and indirect costs by WBS element specified in Attachment `r params$CSDR_plan_attch_numb` - CSDR Plan.  

#### Maintenance and Repair Report
The `r prime_vs_sub` shall prepare and submit the "Maintenance and Repair Report" in accordance with CDRL `r params$SFCHR_CDRL_numb`. The "Maintenance and Repair Report" reports sustainment information including labor hours, parts consumption, overhead costs, material costs, and other direct and indirect cost, by maintenance event, vehicle, part number, and contract line item number.  

#### Technical Data Report (TDR)
The `r prime_vs_sub` shall prepare and submit the "Technical Data Report" in accordance with CDRL `r params$TDR_CDRL_numb`. The "Technical Data Report" reports technical parameter data to provide context to the data reported in FlexFile submissions in order to derive parametric cost estimating relationships.  

#### Software Resources Data Report (SRDR) - Development
The `r prime_vs_sub` shall prepare and submit the "Software Resource Data Report (SRDR)" in accordance with CDRL `r params$SDR_CDRL_numb`. The "Software Resource Data Report (SRDR)" reports expected and actual cost and performance data associated with software development and upgrade efforts.  

#### Software Resources Data Report (SRDR) - Maintenance
The `r prime_vs_sub` shall prepare and submit the "Software Resource Data Report (SRDR)" in accordance with CDRL `r params$SMR_CDRL_numb`. The "Software Resource Data Report (SRDR)" reports expected and actual cost and performance data associated with software maintenance efforts.  

#### Enterprise Resource Planning (ERP) Software Development Report (DD Form 3026-3)
The `r prime_vs_sub` shall prepare and submit the "Enterprise Resource Planning (ERP) Software Development Report (DD Form 3026-3)" in accordance with CDRL `r params$ERP_CDRL_numb`. The "Enterprise Resource Planning (ERP) Software Development Report (DD Form 3026-3)" reports expected and actual cost and performance data associated with the development of ERP systems. 

#### Contract Funds Status Report (CFSR)
The `r prime_vs_sub` shall prepare and submit the "Contract Funds Status Report (CFSR)" in accordance with CDRL `r params$CFSR_CDRL_numb`. The "Contract Funds Status Report (CFSR)" reports data on funding requirements, estimates at completion, a determination of excess funds, and rough estimates of termination costs.  

#### Performance & Cost Report (P&CR)
The `r prime_vs_sub` shall prepare and submit the "Performance & Cost Report (P&CR)" in accordance with CDRL `r params$PaCR_CDRL_numb`. The "Performance & Cost Report (P&CR)" reports data on funding requirements, costs expended, and estimates at completion for work directives and other service efforts.  

#### Lot Size Pricing Data (LSPD) Report
The `r prime_vs_sub` shall collect Lot Size Pricing Data (LSPD) from `r params$acqusition_phase_abbr` subcontractors on all components which are classified either as a Major End Item (MEI) or Component of Interest (CoI), and deliver the "Lot Size Pricing Data (LSPD) Report" to the Government in accordance with CDRL `r params$LSPD_CDRL_numb` and Attachment `r params$LSPD_attach_numb` - Lot Size Pricing Data. The "Lot Size Pricing Data (LSPD) Report" reports information on the expected costs of parts given various procurement quantities and is utilized to estimate rate effects.  

#### Average Unit Manufacturing Cost (AUMC) Report
The `r prime_vs_sub` shall prepare and submit the "Average Unit Manufacturing Cost (AUMC) Report" in accordance with CDRL `r params$AUMC_CDRL_numb` and Attachment `r params$AUMC_attach_numb` - Average Unit Manufacturing Cost (AUMC) Report. The "Average Unit Manufacturing Cost (AUMC) Report" reports non-binding estimates on the `r prime_vs_sub`'s anticipated Average Unit Manufacturing Costs (AUMC) and any `r prime_vs_sub` planned changes to its manufacturing process, end item design, supply chain process, and any other significant planned processes changes that may impact the AUMC of the `r params$system_name_abbr` between the `r params$acqusition_phase_abbr` and a potential `r params$system_name_abbr` follow-on contract, assuming the `r prime_vs_sub` were to be awarded said follow-on contract(s).  

#### Bill of Materials (BOM)
The `r prime_vs_sub` shall prepare and submit the "Bill of Materials (BOM)" in accordance with CDRL `r params$BOM_CDRL_numb` for its `r params$system_name_abbr` design. The "Bill of Materials (BOM)" reports a complete list of material (e.g., part numbers, software, fluids) including all levels of assembly required to build, assemble, and sustain a complete `r params$system_name_abbr` end item to include any kits or appliqué equipment. The first submission of the BOM shall identify the `r prime_vs_sub`'s `r params$system_name_abbr` design as of the date of contract award and the final submission shall identify the `r params$system_name_abbr` design current as of the end of the contract.

#### Post Award Cost and Software Data Reporting Conference
The `r prime_vs_sub` shall host a Post-Award CSDR Conference at the `r prime_vs_sub`’s facility where CSDRs are prepared with the Government’s Cost Working Group Integrated Product Team (CWIPT) IAW DFARS 242.503-2(b) and DoD 5000.04-M-1 (CSDR Manual). The purpose of the Post-Award CSDR Conference is to review the contract’s CSDR requirements and assess how the Contractor’s accounting system satisfies the CSDR requirements found in DoD 5000.04-M-1, “CSDR Manual” and Attachment `r params$CSDR_plan_attch_numb` - CSDR Plan. In a briefing presented by the Contractor in its own format, the Contractor shall:  
- Demonstrate how it collects cost data in its accounting system and how that data will be utilized to provide actual cost transactions and minimize cost allocations when preparing CSDR data deliverables.  
- Describe how recurring vs. nonrecurring costs are segregated in its accounting system and for the purpose of CSDR reporting.  
- Demonstrate how the data from its accounting system will be mapped into the CSDR reports required by Attachment `r params$CSDR_plan_attch_numb` - CSDR Plan and associated CDRLs.  
- Present the methodologies used for mapping internal cost accounts to the WBS, specifically showing how individual WBS elements and functional element codes will be populated.  
- Propose any changes to Attachment `r params$CSDR_plan_attch_numb` - CSDR Plan in order to tailor the plan to the `r prime_vs_sub`’s accounting system, to include any `r prime_vs_sub` recommended changes or additions to the WBS elements. These changes may include adjustments to the submission events and/or submission timelines, particularly in the case of a direct-reporting subcontractor performing against a different delivery schedule than the associated prime contractor.  

The `r prime_vs_sub` and CWIPT will also review the initial submission of the "Resource Distribution Table (RDT)" (CDRL `r params$RDT_CDRL_numb`), in order to finalize which subcontractors will be required to provide CSDR reporting and electronic submission of deliverables directly to the Defense Cost and Resource Center (DCARC) and which subcontractors may qualify for a CSDR direct reporting subcontractor waiver.  

The Post-Award Cost and Software Data Reporting Conference shall be held within 60 days of the Start of Work Meeting on a date mutually agreed to by the CWIPT and the `r prime_vs_sub`. This meeting has an anticipated duration of one business day.  

### CSDR Mapping Review(s)
The `r prime_vs_sub` shall host a CSDR Conference Mapping Review at the `r prime_vs_sub`’s facility where CSDRs are prepared with the Government at least 60 days before the initial CSDR report submission or the second CSDR report submission if the initial submission is due within 60 days of contract award. The purpose of a CSDR Mapping Review is to ensure that all contractor internal control accounts and all part numbers identified in the CDRL `r params$BOM_CDRL_numb` - Bill of Materials (BOM) are mapped to the appropriate CSDR WBS elements in accordance with `r params$CSDR_plan_std` and as required by the CWBS Dictionary `r params$CWBS_CDRL_numb` and Attachment `r params$CSDR_plan_attch_numb` - CSDR Plan. The meeting has an anticipated duration of one business day. In the event that new control accounts or part numbers are created after the initial CSDR Mapping Review, the `r prime_vs_sub` shall review the updated mappings with the Government prior to follow-on CSDR submissions either via phone or email.  
