---
title: "CSDR Section L Language"
output:
  word_document: default
  html_document:
    df_print: paged
version: 0.1.0
---
```{r, eval=FALSE, echo=FALSE}
# Add "IAW Office of Secretary of Defense (OSD) memorandum dated 30 August 2018 titled, "Implementation of Cost Data Reporting Requirements for Middle Tier Acquisition Programs," if being used with an 804 program.
```
L.*.1 The Offeror shall submit the information required by DFARS 252.234-7003, Notice of Cost and Software Data Reporting System, IAW Office of Secretary of Defense (OSD) memorandum dated 22 March 2019 titled, "Implementation of Cost and Hour Report (FlexFile) and Quantity Data Reports Within the Cost and Software Data Reporting (CSDR) System," and as specified below.  

```{r, eval=FALSE, echo=FALSE}
# If Legacy
```
L.*.1.1 In order to comply with the above cited requirements, the Offeror shall utilize the CSDR Plan (Attachment `r params_from_excel$CSDR_plan_attch_numb`) to submit a copy of the following with its proposal in the same format as: 1) Cost Summary Data Report 1921 (CDRL `r params_from_excel$CDSR_CDRL_numb`), 2) Functional Cost-Hour Report 1921-1 (CDRL `r params_from_excel$FCHR_CDRL_numb`), 3) Resource Distribution Table (CDRL `r params_from_excel$RDT_CDRL_numb`). The total reported price within each deliverable submission shall the total value of the Offeror's proposal using the maximum allowable contract quantities, hours, or options (as applicable).  

```{r, eval=FALSE, echo=FALSE}
# If FlexFile
```
L.*.1.1 In order to comply with the above cited requirements, the Offeror shall utilize the CSDR Plan (Attachment `r params_from_excel$CSDR_plan_attch_numb`) to submit a copy of the following with its proposal in the same format as: 1) Cost and Hour Report (FlexFile) (CDRL `r params_from_excel$FlexFile_CDRL_numb`), 2) Quantity Data Report (DD Form 1921-Q) (CDRL `r params_from_excel$QtyData_CDRL_numb`), 3) Resource Distribution Table (CDRL `r params_from_excel$RDT_CDRL_numb`). The total reported price within each deliverable submission shall the total value of the Offeror's proposal using the maximum allowable contract quantities, hours, or options (as applicable).  

L.*.1.2 The Offeror shall submit a report which contains the following:  

(1) Description of the process to be used to satisfy the requirements of the DoD 5000.04-M-1, CSDR Manual, and the Government-approved CSDR plan (Attachment `r params_from_excel$CSDR_plan_attch_numb`) for the proposed contract;  

(2) Demonstration of how contractor cost and data reporting (CCDR) will be based, to the maximum extent possible, upon actual cost transactions and not cost allocations;  

(3) Demonstration of how the data from its accounting system will be mapped into the standard reporting categories required in the CCDR data item descriptions;  

(4) Description of how recurring and nonrecurring costs will be segregated;  

(5) A narrative describing the adequacy of the CSDR contract plan (Attachment `r params_from_excel$CSDR_plan_attch_numb`) and related Resource Distribution Table (Attachment `r params_from_excel$RDT_attach_numb`).  

L.*.1.3 Offerors are advised that information submitted as part of its proposal may be disclosed to the OSD and Department of Army (DA) to support the requirements in OSD Department of Defense (DoD) 5000.04-M-1 - CSDR Manual. The information will be used for the purposes of developing and validating cost estimates and budget submissions in support of the `r params_from_excel$program_name_abbr` program. Information contained within the Offeror's proposal shall be marked in a manner which allows this information to be shared with OSD and DA. An example of such as marking is as follows:

```{r, eval=FALSE, echo=FALSE}
# Note: This is from FAR 52.215-1.
```

"This proposal includes data that shall not be disclosed outside the Government and shall not be duplicated, used, or disclosed -- in whole or in part -- for any purpose other than to evaluate this proposal or support cost estimates and budget submissions in support of the `r params_from_excel$program_name_abbr` program. If, however, a contract is awarded to this Offeror as a result of -- or in connection with -- the submission of this data, the Government shall have the right to duplicate, use, or disclose the data to the extent provided in the resulting contract. This restriction does not limit the Government's right to use information contained in this data if it is obtained from another source without restriction. The data subject to this restriction are contained in sheets [insert numbers or other identification of sheets]."  
